{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Added Structure to Outlook
Equaiton Coherences in proof

@@

	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as (\ref{KarhunenLoeve}). The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:

@@

		Let $K$ be a Hilbert-Schmidt operator as in \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator. With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering

@@

		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since $F(t)$ is the centered process. Now, take the second term

@@

		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in (\ref{HSKernal}). It turns out the product of the eigenfunction and the corresponding eigenvalue. For the last term, we derive from (\ref{Lemma2}) that

@@

		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by (\ref{Thr1}), (\ref{Thr2}), and (\ref{Thr3}) we obtain

>>>>

	\subsection{Limitations}

	\subsection{Possible Extensions}

@@

	\subsection{Lemma} \label{Proof1}
	The curves $X(t) \in \mathbb{L}^2[0,1]$ is expanded by the eigenfunctions $\{\nu^m\}$ as Equation \ref{KarhunenLoeve}. The coefficients $\xi^{m}$ corresponding to eigenfunctions $\nu^m$ satisfy the following properties:

@@

		Let $K$ be a Hilbert-Schmidt operator as in Equation \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator. With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering

@@

		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in Equation \ref{CovarianceFunction} since $F(t)$ is the centered process. Now, take the second term

@@

		where the covariance function $c(t,s)$ has the Hilbert-Schmidt operator as in Equation \ref{HSKernal}. It turns out the product of the eigenfunction and the corresponding eigenvalue. For the last term, we derive from Equation \ref{Lemma2} that

@@

		where $\delta_{m,n} = 1$ if $m=n$, otherwise 0. Therefore, by Equations \ref{Thr1}, \ref{Thr2}, and \ref{Thr3} we obtain
